Conference Paper Critique

### 2019-03-26 conf_paper/paper.tex
critique done, 1.5 pages w/ stupid textwidth, more measurements added

\title{FPGA Based Prototyping of an ADPLL Network\\}

@@

An FPGA as a prototyping tool has seen use in UPMC Sorbonne and University College Dublin, and has been used in the testing of established designs prior to their implementation in custom silicon\cite{zianbetov2013phd,shan2014phd}, the validation of realistic models for use in high level simulations\cite{theboys2019} and the exploration of new designs for digital blocks before progressing on to true digital design on a gate level.  %TODO references

@@

\cite{javidan2011all} proposed the implementation of such a system using All Digital PLLs, which better suited the use cases of the technology and avoided some of the flaws pointed out in the original paper.\\

>>>>

\title{FPGA Based Modelling of an ADPLL Network\\}

@@

An FPGA as a prototyping tool has seen use in UPMC Sorbonne and University College Dublin, and has been used in the testing of established designs prior to their implementation in custom silicon \cite{zianbetov2013phd,shan2014phd}, the validation of realistic models for use in high level simulations\cite{theboys2019} and the exploration of new designs for digital blocks before progressing on to true digital design on a gate level.  %TODO references

@@

\cite{javidan2011all} proposed the implementation of such a system using All Digital PLLs, which better suited the use cases of the technology and avoided some of the flaws pointed out in the original paper. Zianbetov and Shan followed on from this proposition by implementing such a network on a custom IC \cite{zianbetov2013phd,shan2014phd}.\\
